Pillar 1 - Sequential Pattern Mining

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
disables maxwin in clean_IR

### CSPADE Algorithm
We apply cspade algorithm

```{r}
# Transform rules from ruleInduction into a readable data frame
clean_IR <- function(rules){
  rules %>%
    as("data.frame") %>%
    # filter(
    #   count >= 1
    # ) %>%
    mutate(
      rule = str_remove_all(rule, pattern = "[<]"),
      rule = str_remove_all(rule, pattern = "[{]"),
      rule = str_remove_all(rule, pattern = "[}]"),
      rule = str_remove_all(rule, pattern = "[>]"),
      `rhs.support` = confidence / lift
      ) %>%
    separate(rule, into = c("lhs", "rhs"), sep="=") %>%
    mutate_at(
      c("support", #"lhs.support",
        "confidence", "rhs.support", "lift"),
      funs(round(., 5))
    ) %>%
    select(
      lhs, rhs,
      support, 
      #count, lhs.support, #figure out how to get these
      confidence, rhs.support,
      lift
    ) #%>%
    #arrange(
    #  desc(count)
    #)

}
```
We apply cspade followed by rule induction
```{r}
# Run the cspade algorithm with desired parameters. Then run the ruleInduction algorithm with desired parameters.
my_IR <- function(data){
  data %>%
  cspade(
    parameter = list(
      support = 0.01, # min support of a sequence
      maxsize = 1, # max number of items of an element of a sequence
      maxlen  = 2, # max number of element of a sequence
      mingap  = 1, # min time difference between consecutive element of a sequence
      maxgap  = 1e4, # max time difference between consecutive element of a sequence
      maxwin  = 1e4  # max time difference between any two elements of a sequence
      ),
    control = list(
      verbose = FALSE
      )
    ) %>%
    ruleInduction(
      confidence = 0, #we need to play with the parameters.
      control    = list(verbose = FALSE)
      ) %>%
    clean_IR
}

>>>>

### CSPADE Algorithm
We apply cspade algorithm
```{r}
# Transform rules from ruleInduction into a readable data frame
clean_IR <- function(rules){
  rules %>%
    as("data.frame") %>%
    # filter(
    #   count >= 1
    # ) %>%
    mutate(
      rule = str_remove_all(rule, pattern = "[<]"),
      rule = str_remove_all(rule, pattern = "[{]"),
      rule = str_remove_all(rule, pattern = "[}]"),
      rule = str_remove_all(rule, pattern = "[>]"),
      `rhs.support` = confidence / lift
      ) %>%
    separate(rule, into = c("lhs", "rhs"), sep="=") %>%
    mutate_at(
      c("support", #"lhs.support",
        "confidence", "rhs.support", "lift"),
      funs(round(., 5))
    ) %>%
    select(
      lhs, rhs,
      support, 
      #count, lhs.support, #figure out how to get these
      confidence, rhs.support,
      lift
    ) #%>%
    #arrange(
    #  desc(count)
    #)

}
```
We apply cspade followed by rule induction
```{r}
# Run the cspade algorithm with desired parameters. Then run the ruleInduction algorithm with desired parameters.
my_IR <- function(data){
  data %>%
  cspade(
    parameter = list(
      support = 0.01, # min support of a sequence
      maxsize = 1, # max number of items of an element of a sequence
      maxlen  = 2, # max number of element of a sequence
      mingap  = 1, # min time difference between consecutive element of a sequence
      maxgap  = 1e4 # max time difference between consecutive element of a sequence
      #maxwin  = 1e4  # max time difference between any two elements of a sequence # WARNING: 'maxwin' disabled
      ),
    control = list(
      verbose = FALSE
      )
    ) %>%
    ruleInduction(
      confidence = 0, #we need to play with the parameters.
      control    = list(verbose = FALSE)
      ) %>%
    clean_IR
}
